Continuous gravitational waves in the lab: recovering audio signals with a table-top optical microphone

### 2020-09-28 paper/paper_main.tex
small rewording in acknowledgements

\begin{acknowledgments}
The authors are grateful to Jude Prezens, Alex Tolotchkoc, and Blake Molyneux for their technical advice and generous assistance; Patrick Meyers, Margaret Millhouse, Sofia Suvorova for useful discussions; and Patrick Clearwater, Patrick Meyers, Suk Yee Yong, Lucy Strang, Julian Carlin, Sanjaykumar Patil, and Alex Cameron for early work on the interferometer design requirements and construction. 
This research is supported by the Australian Research Council Centre of Excellence for Gravitational Wave Discovery (OzGrav) (project number CE170100004). 
This work received financial support towards hardware from the Institute of Physics International Member Grant and the OzGrav Outreach Support scheme and travel support was received from the Australian National PhB Science program.
This work has been assigned LIGO document number P2000386.

>>>>

\begin{acknowledgments}
The authors are grateful to Jude Prezens, Alex Tolotchkoc, and Blake Molyneux for their technical advice and generous assistance; Patrick Meyers, Margaret Millhouse, Sofia Suvorova for useful discussions; and Patrick Clearwater, Patrick Meyers, Suk Yee Yong, Lucy Strang, Julian Carlin, Sanjaykumar Patil, and Alex Cameron for early work on the interferometer design requirements and construction. 
This research is supported by the Australian Research Council Centre of Excellence for Gravitational Wave Discovery (OzGrav) (project number CE170100004). 
This work received financial support towards hardware from the Institute of Physics International Member Grant and the OzGrav Outreach Support scheme and travel support from the Australian National PhB Science program.
This work has been assigned LIGO document number P2000386.
